\section{Punctured perfectoid open unit disk: A quotient of the punctured\\ unit disk as a diamond and its \'{e}tale fundamental group}
Recall that we constructed the perfectoid space $\tilde{H}^{ad, *}_{C}\!/\pi^{\Z}$ as a quotient of the \emph{punctured perfectoid open unit disk} $\tilde{H}^{ad, *}_{C}$. 

\begin{theorem}\label{firstmainthm}
There is an equivalence of categories between
the category of $\Oo_E^{\times}$-equivariant finite \'{e}tale $\tilde{H}^{ad, *}_{C}\!/\pi^{\Z}$-morphisms and the category of finite \'{e}tale $E$-algebras.
\end{theorem}
\begin{proof}
$\Oo_E^{\times}$-equivariant finite \'{e}tale $\tilde{H}^{ad, *}_{C}\!/\pi^{\Z}$-morphisms correspond to
$E^{\times}$-equivariant finite \'{e}tale $\tilde{H}^{ad, *}_{C}$-morphisms.
$E^{\times}$-equivariant finite \'{e}tale $\tilde{H}^{ad, *}_{C}$-morphisms  correspond to
$E^{\times}$-equivariant finite \'{e}tale $(\tilde{H}^{ad, *}_{C})\tilt$-morphisms by theorem \ref{almostpuritythm} and hence to
$\Oo_E^{\times}\times(\varphi^{-1}\circ Frob_q)^{\Z}$-equivariant finite \'{e}tale 
$\Y_{C\tilt,E}\times\!\!_{\spa{E}{\Oo_E}}\spa{\hat{E}_{\infty}}{\Oo_{\hat{E}_{\infty}}}$-morphisms
by proposition \ref{tiltmainprop} hence to 
$\Oo_E^{\times}\times\varphi^{\Z}$-equivariant finite \'{e}tale 
$\Y_{C\tilt,E}\times\!\!_{\spa{E}{\Oo_E}}\spa{\hat{E}_{\infty}}{\Oo_{\hat{E}_{\infty}}}$-morphisms.
By definition of the adic Fargues-Fontaine curve, these correspond to 
$\Oo_E^{\times}$-equivariant finite \'{e}tale 
$\X_{C\tilt,E}\times\!\!_{\spa{E}{\Oo_E}}\spa{\hat{E}_{\infty}}{\Oo_{\hat{E}_{\infty}}}$-morphisms.
By theorem \ref{gsctheorem} these correspond to
$\Oo_E^{\times}$-equivariant finite \'etale $\hat{E}_{\infty}$-algebras and hence to
finite \'{e}tale $E$-algebras.
\end{proof}

There is an $E^{\times}$-action on $\tilde{H}^{ad, *}_{C}$ and  $\tilde{H}^{ad, *}_{C}\!/\pi^{\Z}$ exists as a perfectoid space. Let us introduce now the main object, namely the following quotient as a sheaf on $\perfc$ for the pro-\'{e}tale topology:
\[Z_E = \tilde{H}^{ad, *}_{C}\!/\underline{E}^{\times}.\]
We consider $\tilde{H}^{ad, *}_{C}\!/\pi^{\Z}$ as the sheaf that the perfectoid space in $\perfc$ represents.
We want to prove the following proposition:

\begin{prop}
The morphism
$\tilde{H}^{ad, *}_{C}\!/\pi^{\Z} \to Z_E$ is a  pro-\'{e}tale $\underline{\Oo_E^\times}$-torsor and a pro-\'{e}tale cover.
In particular $Z_E$ is a diamond.
\end{prop}
\begin{proof}
As in proposition \ref{torsorprop1} we let $\spa{C'}{\Oo_{C'}}\to\spa{C}{\Oo_{C}}$ be a geometric point. Then 
$\tilde{H}^{ad}_{C}(\spa{C'}{\Oo_{C'}})$ is an $E$-vector space, hence the $E^\times$-action on 
$\tilde{H}^{ad, *}_{C}((\spa{C'}{\Oo_{C'}})$, the set of pseudo-uniformizer of ${C'}\tilt$, is free. Hence $\Oo_E^\times$ acts freely on $\tilde{H}^{ad, *}_{C}\!/\pi^{\Z}(\spa{C'}{\Oo_{C'}})$. We then apply proposition \ref{torsorprop1}. This proves the claim.
\end{proof}


\begin{theorem}\label{secondmainthm}
There is an equivalence of categories between the category of finite \'{e}tale $Z_E$-morphisms
 and the
category of finite \'{e}tale $E$-algebras.
\end{theorem}
\begin{proof}
Theorem \ref{torsorthm1} shows that finite \'{e}tale $Z_E$-morphisms are equivalent to $\Oo_E^{\times}$-equivariant finite \'{e}tale $\tilde{H}^{ad, *}_{C}\!/\pi^{\Z}$-morphisms. We then apply theorem \ref{firstmainthm}.

\end{proof}
The category of finite \'{e}tale $Z_E$-morphisms consisting of sheaves on $\perfcsite$ becomes a Galois category.
Hence the associated Galois categories have associated profinite group, the \emph{fundamental group} or group of automorphisms of the fundamental functor, necessarily given by $\pione({\spec{E}})$ with geometric point $\spec{C}$.\\

This proves the formula
\[\pione({Z_E})\simeq\pione({\spec{E}}).\]








\clearpage
\hfill
\clearpage















